\documentclass[margin,line]{res}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\parskip=0.15in

\newcommand{\dated}[2]{\parbox[t]{4.4in}{#1} \hspace{0.4in}
											 \parbox[t]{1in}{ {\it #2 } } }

\begin{document}

\name{John DeNero \vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}lp{4in}}
Google Research            & {\it Phone:} & (415) 203-1943\\
1350 Charleston Road       & {\it Email:} & denero@google.com\\
Mountain View, CA  94043   & {\it Web:}   & http://www.denero.org\\
\end{tabular}

\section{\sc Research Interests}
\dated{Statistical machine translation, natural language processing, machine
learning, and computer science education}{}

\section{\sc Current}
\dated{Research scientist for Google Translate, Mountain View, CA}
{ 2010-present }

\section{\sc Education}
{\bf University of California, Berkeley} \\
\dated{Ph.D., Computer Science \\	
\hspace*{1em} {\it Advisor}: Dan Klein}{ 2005-2010 }

{\bf Stanford University} \\
\dated{Master of Arts, Philosophy\vspace{0.12in}}{ 2001-2002 } \\
\dated{Bachelor of Science, with distinction \\
\hspace*{1em} {\it Major}: Mathematical and Computational Science \\
\hspace*{1em} {\it Secondary Major}: Symbolic Systems}{ 1998-2002 }

\section{\sc Honors and Awards} 
\dated{Google Global Intern Scholarship} { 2009 }

\dated{Teaching Effectiveness Award, UC Berkeley} { 2008 }

\dated{Outstanding Graduate Student Instructor, CS Division} { 2007 }

\dated{Outstanding Graduate Student Instructor, UC Berkeley} { 2007 }

\section{\sc Teaching Experience}
\dated{ {\bf Primary Course Instructor}\\
Instructor for CS 188: Introduction to Artificial Intelligence, a 95 student
upper-division course. Delivered 27 lectures, managed a 7-person course staff,
and created all projects, assignments, and exams.} {Spring 2009} \\

\dated{ {\bf Graduate Student Instructor}}{Fa '05, Sp '06}\\
\dated{ Support staff for CS 188 in charge of discussion sections, labs, review
sessions, and course projects.}
{Fa '06, Fa '07} \\

\dated{ {\bf Tutorial Instructor }\\
Lecturer and project designer for a tutorial in machine translation during the
Summer Workshop of the Center for Language and Speech Processing at Johns
Hopkins University, co-taught with Adam Lopez. }
{Sum '09 \& '10}

\section{\sc Publications}

{\bf Thesis }

John DeNero. ``Phrase Alignment Models for Statistical Machine Translation,'' in {\it Ph.D. Dissertation in Computer Science, UC Berkeley}, 2010. 

{\bf Refereed Publications }

John DeNero and Klaus Machery. ``Model-Based Aligner Combination Using Dual Decomposition,'' in {\it Proceedings of the Association of Computational Linguistics}, 2011. 

John DeNero and Dan Klein. ``Discriminative Modeling of Extraction Sets for Machine Translation,'' in {\it Proceedings of the Association of Computational Linguistics}, 2010. 

John DeNero, Shankar Kumar, Ciprian Chelba, and Franz Och. ``Model Combination for Machine Translation,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2010. 

John DeNero and Dan Klein. ``Teaching Introductory Artificial Intelligence with Pac-Man,'' in {\it Proceedings of the Symposium on Educational Advances in Artificial Intelligence}, 2010. 

John DeNero and Dan Klein. ``The Pac-Man Projects Software Package for Introductory Artificial Intelligence,'' in {\it Proceedings of the Symposium on Educational Advances in Artificial Intelligence, Model Assignments Track}, 2010. 

Taylor Berg-Kirkpatrick, Alexandre Bouchard-Côté, John DeNero, and Dan Klein. ``Painless Unsupervised Learning with Features,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2010. 

John DeNero, David Chiang, and Kevin Knight. ``Fast Consensus Decoding over Translation Forests,'' in {\it Proceedings of the Association of Computational Linguistics}, 2009. 

Adam Pauls, John DeNero, and Dan Klein. ``Consensus Training for Consensus Decoding in Machine Translation,'' in {\it Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 2009. 

John DeNero, Adam Pauls, and Dan Klein. ``Asynchronous Binarization for Synchronous Grammars,'' in {\it Proceedings of the Association of Computational Linguistics, Short Paper Track}, 2009. 

Aria Haghighi, John Blitzer, John DeNero, and Dan Klein. ``Better Word Alignments with Supervised ITG Models,'' in {\it Proceedings of the Association of Computational Linguistics}, 2009. 

John DeNero, Mohit Bansal, Adam Pauls, and Dan Klein. ``Efficient Parsing for Transducer Grammars,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2009. 

John DeNero, Alex Bouchard-Côté, and Dan Klein. ``Sampling Alignment Structure under a Bayesian Translation Model,'' in {\it Proceedings of the Conference on Empirical Methods in Natural Language Processing}, 2008. 

John DeNero and Dan Klein. ``The Complexity of Phrase Alignment Models,'' in {\it Proceedings of the Association of Computational Linguistics, Short Paper Track}, 2008. 

John DeNero and Alexandre Bouchard. ``A Hierarchical Dirichlet Process Prior for a Conditional Model of Phrase Alignment,'' in {\it the Workshop on Unsupervised Models in NLP, Neural and Information Processing Systems}, 2008. 

Aria Haghighi, John DeNero, and Dan Klein. ``A* Search via Approximate Factoring,'' in {\it Proceedings of American Association of Artificial Intelligence, Nectar Track}, 2007. 

John DeNero and Dan Klein. ``Tailoring Word Alignments to Syntactic Machine Translation,'' in {\it Proceedings of the Association of Computational Linguistics}, 2007. 

Aria Haghighi, John DeNero, and Dan Klein. ``Approximate Factoring for A* Search,'' in {\it Proceedings of the North American Association of Computational Linguistics}, 2007. 

John DeNero, Dan Gillick, James Zhang, and Dan Klein. ``Why Generative Phrase
Models Underperform Surface Heuristics,'' in {\it Proceedings of the Workshop on
Statistical MT}, 2006. 

\section{\sc Invited Talks }
\dated{Invited Research Talk, Google Research}{2010} \\
{\em Host}: Jay Ponte

\dated{Invited Research Talk, Yahoo! Research}{2010} \\
{\em Host}: Patrick Pantel

\dated{Invited Research Talk, Microsoft Research}{2010} \\
{\em Host}: Robert Moore

\dated{Invited Research Talk, Toyota Technological Institute, Chicago}{2010} \\
{\em Host}: Karen Livescu

\dated{Invited Research Talk, New York University}{2010} \\
{\em Host}: Richard Cole

\dated{Invited Research Talk, Johns Hopkins University}{2010} \\
{\em Host}: Mark Dredze 

\dated{Invited Research Talk, University of Maryland}{2010} \\
{\em Host}: Jimmy Lin 

\dated{Guest Lecture, UC Berkeley, Applied Natural Language Processing}{2009} \\
{\em Host}: Barbara Rosario 

\dated{Invited Research Talk, Yahoo! Research}{2008} \\
{\em Host}: Patrick Pantel 

\dated{Invited Research Talk, Information Sciences Institute}{2008} \\
{\em Host}: Kevin Knight 

\dated{Invited Research Talk, International Computer Science Institute}{2008} \\
{\em Host}: Dilek Hakkani-T\"{u}r 

\dated{Invited Research Talk, Microsoft Research Asia}{2008} \\
{\em Host}: Mu Li 

\dated{Invited Research Talk, SRI International}{2008} \\
{\em Host}: Jing Zheng 

\section{\sc Experience}

\dated{ {\bf Google Research}, Mountain View, CA\\
Research intern for Google Translate.  Developed a method for combining
heterogeneous machine translation models. \\
{\em Hosts}: Jay Ponte and Shankar Kumar
}{Summer 2009} \\

\dated{ {\bf Information Sciences Institute}, Marina del Rey, CA \\
Research intern in machine translation. Developed a forest-based consensus
decoding technique for hierarchical machine translation systems. \\
{\em Hosts}: David Chiang and Kevin Knight}{Summer 2008} \\

\dated{ {\bf McKinsey \& Company}, San Francisco, CA \\
Business analyst for general management consulting projects in sourcing, human
resources, risk-based pricing, and product strategy.}{2003-2004}

\newpage

\section{\sc Professional Activities}

{\bf Conference Reviewer}: EMNLP '08, NAACL '09, ACL '09, EMNLP '09, MT Summit
'09,\\ NAACL '10, ACL '10, COLING '10, ACL '11, AAAI '11, EMNLP '11. 

\section{\sc Software}

{\bf The Pacman Projects} \\
A series of five course projects that introduce students to core artificial
intelligence concepts in an engaging and open-ended problem setting. Projects
culminate in an intercollegiate agent-building competition. The projects have
been shared with faculty at over 30 colleges and universities.\\
{\it http://inst.eecs.berkeley.edu/~cs188/sp09/pacman.html }

{\bf The Berkeley Aligner } \\
A word alignment package for machine translation that implements agreement-based
learning and a syntax-sensitive alignment model, authored and maintained with
Percy Liang. The software has been downloaded over 4,000 times. \\
{\it http://code.google.com/p/berkeleyaligner }

\end{resume}
\end{document}




